---
title: "Anscombe's Quartet of ‘Identical’ Simple Linear Regressions"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: The descriptions has been taken from R.

## Description

Four x-y datasets which have the same traditional statistical properties (mean, variance, correlation, regression line, etc.), yet are quite different.

## Usage

```{r}
head(anscombe)
```

## Format

A data frame with 11 observations on 8 variables.

**Variable** | **Meaning**
-------------|---------------------------------------------------------------------------------------
x1           | X for linear relationship
x2           | X for non-linear relationship
x3    	     | X for outlier	
x4    	     | X for constant
y1    	     | Y for linear relationship
y2    	     | Y for non-linear relationship	
y3    	     | Y for outlier
y4    	     | Y for constant

```{r, echo=FALSE}
library("lattice")
dn <- c("x1-y1", "x2-y2", "x3-y3", "x4-y4")
dxy<-data.frame(dataset=dn[1+(0:43)/11],
                x=c(anscombe$x1, anscombe$x2, anscombe$x3, anscombe$x4),
                y=c(anscombe$y1, anscombe$y2, anscombe$y3, anscombe$y4))
xyplot(y~x|dataset, data=dxy)
```

## Source

* Tufte, Edward R. (1989). The Visual Display of Quantitative Information, 13–14. Graphics Press.

## References

* Anscombe, Francis J. (1973). Graphs in statistical analysis. The American Statistician, 27, 17–21. doi: 10.2307/2682899.
