---
title: "Housing Values in Suburbs of Boston"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: The descriptions has been taken from R.

## Boston Housing Data in the library `MASS`

### Description

The Boston data frame has 506 rows and 14 columns.

### Usage

```{r}
data(Boston, package="MASS")
head(Boston)
```

### Format

This data frame contains the following columns:

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
crim         | per capita crime rate by town.
zn           | proportion of residential land zoned for lots over 25,000 sq.ft.
indus        | proportion of non-retail business acres per town.
chas         | Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).
nox          | nitrogen oxides concentration (parts per 10 million).
rm           | average number of rooms per dwelling.
age          | proportion of owner-occupied units built prior to 1940.
dis          | weighted mean of distances to five Boston employment centres.
rad          | index of accessibility to radial highways.
tax          | full-value property-tax rate per \$10,000.
ptratio      | pupil-teacher ratio by town.
black        | 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.
lstat        | lower status of the population (percent).
medv         | median value of owner-occupied homes in \$1000s.

### References

* Harrison, D. and Rubinfeld, D.L. (1978) Hedonic prices and the demand for clean air. J. Environ. Economics and Management 5, 81–102.
* Belsley D.A., Kuh, E. and Welsch, R.E. (1980) Regression Diagnostics. Identifying Influential Data and Sources of Collinearity. New York: Wiley.

## Boston Housing Data in the library `spData`

### Description

The `boston.c` data frame has 506 rows and 20 columns. It contains the Harrison and Rubinfeld (1978) data corrected for a few minor errors and augmented with the latitude and longitude of the observations. Gilley and Pace also point out that MEDV is censored, in that median values at or over USD 50,000 are set to USD 50,000. 

### Usage

```{r}
data(boston, package="spData")
head(boston.c)
```

### Format

This data frame contains the following columns:

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
TOWN         | a factor with levels given by town names
TOWNNO       | a numeric vector corresponding to TOWN
TRACT        | a numeric vector of tract ID numbers
LON          | a numeric vector of tract point longitudes in decimal degrees
LAT          | a numeric vector of tract point latitudes in decimal degrees
MEDV         | a numeric vector of median values of owner-occupied housing in USD 1000
CMEDV        | a numeric vector of corrected median values of owner-occupied housing in USD 1000
CRIM         | a numeric vector of per capita crime
ZN           | a numeric vector of proportions of residential land zoned for lots over 25000 sq. ft per town (constant for all Boston tracts)
INDUS        | a numeric vector of proportions of non-retail business acres per town (constant for all Boston tracts)
CHAS         | a factor with levels 1 if tract borders Charles River; 0 otherwise
NOX          | a numeric vector of nitric oxides concentration (parts per 10 million) per town
RM           | a numeric vector of average numbers of rooms per dwelling
AGE          | a numeric vector of proportions of owner-occupied units built prior to 1940
DIS          | a numeric vector of weighted distances to five Boston employment centres
RAD          | a numeric vector of an index of accessibility to radial highways per town (constant for all Boston tracts)
TAX          | a numeric vector full-value property-tax rate per USD 10,000 per town (constant for all Boston tracts)
PTRATIO      | a numeric vector of pupil-teacher ratios per town (constant for all Boston tracts)
B            | a numeric vector of 1000*(Bk - 0.63)^2 where Bk is the proportion of blacks
LSTAT        | a numeric vector of percentage values of lower status population

### Source

http://lib.stat.cmu.edu/datasets/boston_corrected.txt

### References

* Harrison, David, and Daniel L. Rubinfeld, Hedonic Housing Prices and the Demand for Clean Air, Journal of Environmental Economics and Management, Volume 5, (1978), 81-102. Original data.
* Gilley, O.W., and R. Kelley Pace, On the Harrison and Rubinfeld Data, Journal of Environmental Economics and Management, 31 (1996),403-405. Provided corrections and examined censoring.
* Pace, R. Kelley, and O.W. Gilley, Using the Spatial Configuration of the Data to Improve Estimation, Journal of the Real Estate Finance and Economics, 14 (1997), 333-340.
* Bivand, Roger. Revisiting the Boston data set - Changing the units of observation affects estimated willingness to pay for clean air. REGION, v. 4, n. 1, p. 109-127, 2017. http://openjournals.wu.ac.at/ojs/index.php/region/article/view/107.