---
title: "Concrete"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

Data about concrete mixtures and resulting properties (Slump, Flow and Strength). Input variables are:

__Water content__ 
: ACI 211.1 (Standard practice for selecting proportions for normal, heavyweight, and mass concrete) assumes that, for a given maximum size of coarse aggregate, the slump or consistency of concrete is a direct function of the water content; i.e., within limits it is independent of other factors such as aggregate grading and cement content.

__Superplasticizer__
: When the water content of a concrete mixture is held constant, the addition of a superplasticizer will increase the consistency.

__Pozzolanic admixtures__
: Pozzolanic admixtures tend to improve the cohesiveness of concrete. Fly ash, when used as a partial replacement for fine aggregate, generally increases the consistency at a given water content.

__Cement content__
: Concretes containing a very high proportion of cement show excellent cohesiveness, but tend to be sticky. At a given water content, a considerable lowering of the cement content tends to produce harsh mixtures, with poor cohesiveness.

__Aggregate characteristics__
: Very fine sands require more water for a given consistency; alternatively, they will produce harsh and unworkable mixtures at a water content that might have been adequate with coarser sands. Also, the particle size of coarse aggregate influences the water requirement for a given consistency.

## Usage

```{r}
library("rio")
#concrete <- import("https://shinyapps.hu-berlin.de/u/stat/data/concrete.sav")
#head(concrete)
```

## Format

The data set contains data of 237 children between 11 and 20 years.

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
Cement       | Cement (in kg/m$^3$ concrete)
Slag         | Slag (in kg/m$^3$ concrete)
Flyash       | Fly ash (in kg/m$^3$ concrete)
Water        | Water (in kg/m$^3$ concrete)
SP           | Superplasticizer (in kg/m$^3$ concrete)
CoarseAggr   | Coarse sand (in kg/m$^3$ concrete)
FineAggr     | Fine sand (in kg/m$^3$ concrete)
Slump        | Slump (in cm)
Flow         | Flow (in cm)
Strength     | 28day compressive strength (in Megapascal) 

## Source

* [Concrete Slump Test Data Set](https://archive.ics.uci.edu/ml/datasets/Concrete+Slump+Test) from the UCI Machine Learning Repository

## References

* Yeh, I-Cheng (2007) Modeling slump flow of concrete using second-order regressions and 
	artificial neural networks, Cement and Concrete Composites, Vol.29, No. 6, 474-480. https://doi.org/10.1016/j.cemconcomp.2007.02.001
