---
title: "Current Population Survey 1978 & 1985"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: The descriptions has been taken from R.

## Description

The Current Population Survey (CPS) is used to supplement census information between census years. These data consist of a random sample of persons from the CPS78 and CPS85, with information on wages and other characteristics of the workers, including sex, number of years of education, years of work experience, occupational status, region of residence and union membership. 

## Usage

```{r}
library("rio")
#cps <- import("https://shinyapps.hu-berlin.de/u/stat/data/cps_78_85.sav")
#head(cps)
```

## Format

The data set contains data of 237 children between 11 and 20 years.

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
educ         | Number of years of education
south        | Indicator variable for Southern Region 
nonwhite     | Indicator variable for non-whites
female       | Indicator variable for sex
married      | Marital Status 
exper        | Number of years of work experience
expersq      | Number of years of work experience squared
union        | Indicator variable for union membership
lwage        | Log(Wage), wage in dollars per hour
age          | Age (years)
year         | Year of survey, either 78 or 85

## Source

* Modified version from [Statlib](http://lib.stat.cmu.edu/datasets/CPS_85_Wages )

## References

Berndt, E.R. (1991). The Practice of Econometrics. New York: Addison-Wesley. 
