---
title: "Datasaurus Dozen data"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: The descriptions has been taken from R.

## Description

A dataset demonstrating the utility of visualization. These 13 datasets are equal in standard measures: mean, standard deviation, and Pearson's correlation.

## Usage

```{r}
library("datasauRus")
head(datasaurus_dozen)
```

## Format

A data frame with 1846 rows and 3 variables:

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
dataset      | indicates which dataset the data are from
x            | x-values
y            | y-values

```{r, echo=FALSE}
library("lattice")
xyplot(y~x|dataset, data=datasaurus_dozen, pch=19, cex=0.5)
``` 

## Source

* Matejka, J., & Fitzmaurice, G. (2017). Same Stats, Different Graphs: Generating Datasets with Varied Appearance and Identical Statistics through Simulated Annealing. CHI 2017 Conference proceedings: ACM SIGCHI Conference on Human Factors in Computing Systems. Retrieved from https://www.autodeskresearch.com/publications/samestats.