---
title: "Life expectancy 1992"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

Data execerpt of General Social Survey in 1992.

## Usage

```{r}
library("rio")
#x <- import("https://shinyapps.wiwi.hu-berlin.de/u/stat/data/gss92.sav")
#head(x)
```

## Format

The data set contains 1500 observations and 49 variables. The following exercept describes only variables used in the lecture Data analysis I+II.

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
age          | Age of Respondent
sex          | Respondent's Sex (1=Male, 2=Female)
educ         | Highest Year of School Completed 
sibs         | Number of brothers and sisters
life         | Is life dull (=1), routine (=2) or exciting (=3)
speduc       | Highest Year of School Completed by Spouse
paeduc       | Highest Year of School Completed by Father
maeduc       | Highest Year of School Completed by Mother
tvhours      | Hours of Television Watched
wrkstat      | Labor Force Status (1=Working fulltime)
hrs1         | Number of Hours Worked Last Week
rincmdol     | Respondent's Income (in US\$)
wifeduc      | Wife: number of years of education
husbeduc     | Husband: number of years of education
wifeft       | Wife employed full time (0=No, 1=Yes)
happy        | General happiness (1=Very Happy, 2=Pretty happy, 3=Not too happy, NA=NAP/DK/NA)
hapmar       | Happiness of marriage (coding as in happy)

## Source

* Norušis, Marija J. IBM SPSS Statistics 19: Guide to Data Analysis. Internat. ed. Upper Saddle River: Prentice Hall, 2011. http://www.norusis.com/book_DA_v19.php
