---
title: "Life expectancy 1992"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

Data about life expectancy and health system indicators for countries in 1992.

## Usage

```{r}
library("rio")
#x <- import("https://shinyapps.wiwi.hu-berlin.de/u/stat/data/country.sav")
#head(x)
```

## Format

The data set contains data about 122 countries in 1992

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
COUNTRY      | Country name
POP92        | Population, 1992, in millions
URBAN        | Percent urban, 1992
GDP          | GDP per capita
LIFEEXPM     | Male life expectancy 1992
LIFEEXPF     | Female life expectancy 1992
BIRTHRAT     | Births per 1000 population, 1992
DEATHRAT     | Deaths per 1000 people, 1992
INFMR        | Infant mortality rate 1992 (per 1000 live births)
FERTRATE     | Fertility rate per woman, 1990
REGION       | Region of the world (1=Eastern Africa, 2=Middle Africa, 3=Northern Africa, 4=Southern Africa, 5=Western Africa, 6=Caribbean, 7=Central America, 8=South America, 9=North America, 10=Eastern Asia, 11=Southeast Asia, 12=Southern Asia, 13=Western Asia, 14=Eastern Europe, 15=Northern Europe, 16=Southern Europe, 17=Western Europe, 18=Oceania, 19=USSR) 
DEVELOP      | Status as Developing Country (0=Developed country, 1=Developing country)
RADIO        | Radios per 100 people
PHONE        | Phones per 100 people
HOSPBED      | Hospital beds per 10,000 people
DOCS         | Doctors per 10,000 people
LNDOCS       | Natural log of doctors per 10000
LNRADIO      | Natural log of radios per 100 people
LNPHONE      | Natural log of phones per 100 people
LNGDP        | Natural log of GDP
SEQUENCE     | Arbitrary sequence number
LNBEDS       | Natural log hospital beds/10,000

## Source

* Norušis, Marija J. IBM SPSS Statistics 19: Guide to Data Analysis. Internat. ed. Upper Saddle River: Prentice Hall, 2011. http://www.norusis.com/book_DA_v19.php
