---
title: "Olypmpic Decathlon"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    includes:
      before_body: header_sk.html    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: The descriptions has been taken from R.

## Description

This data set gives the performances of 33 men's decathlon at the Olympic Games (1988).

## Usage

```{r}
data(olympic, package="ade4")
head(olympic$tab)
head(olympic$score)
```

## Format

`olympic` is a list of 2 components: a data frame with 33 rows and 10 columns events of the decathlon and a vector of the final points scores of the competition.

**Variable** | **Meaning**
-------------|-----------------------------------------------------------------------------------------
tab$100      | 100 meters / 100 Meter Lauf
tab$long     | long jump / Weitsprung
tab$poid     | shotput / Kugelstoßen
tab$haut     | high jump / Hochsprung
tab$400      | 400 meters / 400 Meter Lauf
tab$110      | 110-meter hurdles / 110 Meter Hürdenlauf
tab$disq     | discus throw / Diskuswurf
tab$perc     | pole vault / Stabhochsprung
tab$jave     | javelin / Speerwurf
tab$1500     | 1500 meters / 1500 Meter Lauf
score        | score / Punkte

## Source

* Example 357 in: Hand, D.J., Daly, F., Lunn, A.D., McConway, K.J. and Ostrowski, E. (1994) A handbook of small data sets, Chapman & Hall, London. 458 p.
* Lunn, A. D. and McNeil, D.R. (1991) Computer-Interactive Data Analysis, Wiley, New York
